Temporal Activity Detection in Untrimmed Videos with RNN

### 2016-10-14 paper.tex
Add note
Update on Overleaf.

\author{
    Alberto Montes \\
    Polytechnic University of Catalonia \\
    Barcelona, Catalonia/Spain \\
    \texttt{al.montes.gomez@gmail.com} \\
    \And
    Amaia Salvador \\
    Image Processing Group \\
    Polytechnic University of Catalonia \\
    Barcelona, Catalonia/Spain \\
    \texttt{amaia.salvador@upc.edu} \\
    \And
    Xavi Giro-i-Nieto \\
    Image Processing Group \\
    Polytechnic University of Catalonia \\
    Barcelona, Catalonia/Spain \\
    \texttt{xavier.giro@upc.edu} \\
}

@@

Explain conclusion

>>>>

\author{
    Alberto Montes \\
    Polytechnic University of Catalonia \\
    Barcelona, Catalonia/Spain \\
    \texttt{al.montes.gomez@gmail.com} \\
    \And
    Amaia Salvador \\
    Image Processing Group \\
    Polytechnic University of Catalonia \\
    Barcelona, Catalonia/Spain \\
    \texttt{amaia.salvador@upc.edu} \\
    \And
    Xavier Giro-i-Nieto \\
    Image Processing Group \\
    Polytechnic University of Catalonia \\
    Barcelona, Catalonia/Spain \\
    \texttt{xavier.giro@upc.edu} \\
}

@@

Explain conclusions. Give at the footnote to the repo where all the code is available.
